### 2017-01-15 results.tex
arxiv submission

\begin{figure}[!ht]
\centering
\includegraphics[width=0.49\linewidth]{png/cos-small.pdf}
\includegraphics[width=0.49\linewidth]{png/cos-big.pdf}
\caption{Degradation in squared error after pruning a two-layer network trained to compute the cosine function (\textbf{Left Network:} 2 layers, 10 neurons each, 1 output, logistic sigmoid activation, starting test accuracy: 0.9999993, \textbf{Right Network:} 2 layers, 50 neurons each, 1 output, logistic sigmoid activation, starting test accuracy: 0.9999996)}
\label{fig:cosine-double-layer}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.49\linewidth]{png/mnist-acc99-single-pass-method.pdf}
\includegraphics[width=0.49\linewidth]{png/mnist-acc99-single-pass-accuracy.pdf}
\caption{Degradation in squared error (left) and classification accuracy (right) after pruning a single-layer network using The Single Overall Ranking algorithm (\textbf{Network:} 1 layer, 100 neurons, 10 outputs, logistic sigmoid activation, starting test accuracy: 0.998)}
\label{fig:mnist-single-ranking-single-layer}
\end{figure}

@@

\subsubsection{Iterative Re-Ranking Algorithm}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.49\linewidth]{png/mnist-acc99-iterative-rerank-method.pdf}
\includegraphics[width=0.49\linewidth]{png/mnist-acc99-iterative-rerank-accuracy.pdf}
\caption{Degradation in squared error (left) and classification accuracy (right) after pruning a single-layer network the iterative re-ranking algorithm (\textbf{Network:} 1 layer, 100 neurons, 10 outputs, logistic sigmoid activation, starting test accuracy: 0.998)}
\label{fig:mnist-re-ranking-single-layer}
\end{figure}

@@

\subsubsection{Visualization of brute force Pruning Decisions}
\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{png/mnist-acc99-gt-gain.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the brute force criterion; (\textbf{Network:} 1 layer, 100 neurons, 10 outputs, logistic sigmoid activation, starting test accuracy: 0.998)}
\label{fig:mnist-single-layer-gt}
\end{figure}

@@

\subsubsection{Visualization of 1st Order Approximation Pruning Decisions}
\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{png/mnist-acc99-g1-gain.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the 1st order Taylor Series error approximation criterion; (\textbf{Network:} 1 layer, 100 neurons, 10 outputs, logistic sigmoid activation, starting test accuracy: 0.998)}
\label{fig:mnist-single-layer-g1}
\end{figure}

@@

\subsubsection{Visualization of 2nd Order Approximation Pruning Decisions}
\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{png/mnist-acc99-g2-gain.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the 2nd order Taylor Series error approximation criterion; (\textbf{Network:} 1 layer, 100 neurons, 10 outputs, logistic sigmoid activation, starting test accuracy: 0.998)}
\label{fig:mnist-single-layer-g2}
\end{figure}

@@

\subsubsection{Single Overall Ranking Algorithm}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.49\linewidth]{png/mnist-deep-single-pass-method.pdf}
\includegraphics[width=0.49\linewidth]{png/mnist-deep-single-pass-accuracy.pdf}
\caption{Degradation in squared error (left) and classification accuracy (right) after pruning a 2-layer network using the Single Overall Ranking algorithm; (\textbf{Network:} 2 layers, 50 neurons/layer, 10 outputs, logistic sigmoid activation, starting test accuracy: 1.000)}
\label{fig:mnist-single-ranking-double-layer}
\end{figure}

@@

\subsubsection{iterative re-ranking Algorithm}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.49\linewidth]{png/mnist-deep-iterative-rerank-method.pdf}
\includegraphics[width=0.49\linewidth]{png/mnist-deep-iterative-rerank-accuracy.pdf}
\caption{Degradation in squared error (left) and classification accuracy (right) after pruning a 2-layer network using the iterative re-ranking algorithm; (\textbf{Network:} 2 layers, 50 neurons/layer, 10 outputs, logistic sigmoid activation, starting test accuracy: 1.000)}
\label{fig:mnist-re-ranking-double-layer}
\end{figure}

@@

\subsubsection{Visualization of brute force Pruning Decisions}
\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{png/mnist-deep-gt-gain.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the brute force criterion; (\textbf{Network:} 2 layers, 50 neurons/layer, 10 outputs, logistic sigmoid activation, starting test accuracy: 1.000)}
\label{fig:mnist-gt-double-layer}
\end{figure}

@@

\subsubsection{Visualization of 1st Order Approximation Pruning Decisions}
\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{png/mnist-deep-g1-gain.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the 1st order Taylor Series error approximation criterion; (\textbf{Network:} 2 layers, 50 neurons/layer, 10 outputs, logistic sigmoid activation, starting test accuracy: 1.000)}
\label{fig:mnist-g1-double-layer}
\end{figure}

@@

\subsubsection{Visualization of 2nd Order Approximation Pruning Decisions}
\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{png/mnist-deep-g2-gain.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the 2nd order Taylor Series error approximation criterion; (\textbf{Network:} 2 layers, 50 neurons/layer, 10 outputs, logistic sigmoid activation, starting test accuracy: 1.000)}
\label{fig:mnist-g2-double-layer}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\linewidth]{png/mnist-test-single-digit-0.pdf}
\caption{Degradation in squared error after pruning a single-layer network trained to do a one-versus-all classification of the digit 0 using the iterative re-ranking algorithm}
\label{fig:mnist-test-single-digit-0}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{png/mnist-test-single-digit-0-gt.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the brute force iterative re-ranking removal criterion}
\label{fig:mnist-test-single-digit-0-gt}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{png/mnist-test-single-digit-0-g1.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the first-order iterative re-ranking removal criterion}
\label{fig:mnist-test-single-digit-0-g1}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{png/mnist-test-single-digit-0-g2.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the second-order iterative re-ranking removal criterion}
\label{fig:mnist-test-single-digit-0-g2}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\linewidth]{png/mnist-test-single-digit-1.pdf}
\caption{Degradation in squared error after pruning a single-layer network trained to do a one-versus-all classification of the digit 1 using the iterative re-ranking algorithm}
\label{fig:mnist-test-single-digit-1}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{png/mnist-test-single-digit-1-gt.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the brute force iterative re-ranking removal criterion}
\label{fig:mnist-test-single-digit-1-gt}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{png/mnist-test-single-digit-1-g1.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the first-order iterative re-ranking removal criterion}
\label{fig:mnist-test-single-digit-1-g1}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{png/mnist-test-single-digit-1-g2.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the second-order iterative re-ranking removal criterion}
\label{fig:mnist-test-single-digit-1-g2}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\linewidth]{png/mnist-test-single-digit-2.pdf}
\caption{Degradation in squared error after pruning a single-layer network trained to do a one-versus-all classification of the digit 2 using the iterative re-ranking algorithm}
\label{fig:mnist-test-single-digit-2}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{png/mnist-test-single-digit-2-gt.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the brute force iterative re-ranking removal criterion}
\label{fig:mnist-test-single-digit-2-gt}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{png/mnist-test-single-digit-2-g1.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the first-order iterative re-ranking removal criterion}
\label{fig:mnist-test-single-digit-2-g1}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{png/mnist-test-single-digit-2-g2.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the second-order iterative re-ranking removal criterion}
\label{fig:mnist-test-single-digit-2-g2}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.49\linewidth]{png/diamond-iterative-rerank-method.pdf}
\includegraphics[width=0.49\linewidth]{png/diamond-iterative-rerank-accuracy.pdf}
\includegraphics[width=0.49\linewidth]{png/rshape-iterative-rerank-method.pdf}
\includegraphics[width=0.49\linewidth]{png/rshape-iterative-rerank-accuracy.pdf}
\caption{Degradation in squared error (left) and classification accuracy (right) after pruning a 2-layer network using the iterative re-ranking algorithm on a toy ``diamond'' shape dataset (top) and a toy ``random shape'' dataset (below); (\textbf{Network:} 2 layers, 50 neurons/layer, 10 outputs, logistic sigmoid activation, starting test accuracy: 0.992(diamond); 0.986(random shape)}
\label{fig:diamond}
\end{figure}

>>>>

\begin{figure}[!ht]
\centering
\includegraphics[width=0.49\linewidth]{cos-small.pdf}
\includegraphics[width=0.49\linewidth]{cos-big.pdf}
\caption{Degradation in squared error after pruning a two-layer network trained to compute the cosine function (\textbf{Left Network:} 2 layers, 10 neurons each, 1 output, logistic sigmoid activation, starting test accuracy: 0.9999993, \textbf{Right Network:} 2 layers, 50 neurons each, 1 output, logistic sigmoid activation, starting test accuracy: 0.9999996)}
\label{fig:cosine-double-layer}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.49\linewidth]{mnist-acc99-single-pass-method.pdf}
\includegraphics[width=0.49\linewidth]{mnist-acc99-single-pass-accuracy.pdf}
\caption{Degradation in squared error (left) and classification accuracy (right) after pruning a single-layer network using The Single Overall Ranking algorithm (\textbf{Network:} 1 layer, 100 neurons, 10 outputs, logistic sigmoid activation, starting test accuracy: 0.998)}
\label{fig:mnist-single-ranking-single-layer}
\end{figure}

@@

\subsubsection{Iterative Re-Ranking Algorithm}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.49\linewidth]{mnist-acc99-iterative-rerank-method.pdf}
\includegraphics[width=0.49\linewidth]{mnist-acc99-iterative-rerank-accuracy.pdf}
\caption{Degradation in squared error (left) and classification accuracy (right) after pruning a single-layer network the iterative re-ranking algorithm (\textbf{Network:} 1 layer, 100 neurons, 10 outputs, logistic sigmoid activation, starting test accuracy: 0.998)}
\label{fig:mnist-re-ranking-single-layer}
\end{figure}

@@

\subsubsection{Visualization of brute force Pruning Decisions}
\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{mnist-acc99-gt-gain.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the brute force criterion; (\textbf{Network:} 1 layer, 100 neurons, 10 outputs, logistic sigmoid activation, starting test accuracy: 0.998)}
\label{fig:mnist-single-layer-gt}
\end{figure}

@@

\subsubsection{Visualization of 1st Order Approximation Pruning Decisions}
\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{mnist-acc99-g1-gain.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the 1st order Taylor Series error approximation criterion; (\textbf{Network:} 1 layer, 100 neurons, 10 outputs, logistic sigmoid activation, starting test accuracy: 0.998)}
\label{fig:mnist-single-layer-g1}
\end{figure}

@@

\subsubsection{Visualization of 2nd Order Approximation Pruning Decisions}
\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{mnist-acc99-g2-gain.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the 2nd order Taylor Series error approximation criterion; (\textbf{Network:} 1 layer, 100 neurons, 10 outputs, logistic sigmoid activation, starting test accuracy: 0.998)}
\label{fig:mnist-single-layer-g2}
\end{figure}

@@

\subsubsection{Single Overall Ranking Algorithm}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.49\linewidth]{mnist-deep-single-pass-method.pdf}
\includegraphics[width=0.49\linewidth]{mnist-deep-single-pass-accuracy.pdf}
\caption{Degradation in squared error (left) and classification accuracy (right) after pruning a 2-layer network using the Single Overall Ranking algorithm; (\textbf{Network:} 2 layers, 50 neurons/layer, 10 outputs, logistic sigmoid activation, starting test accuracy: 1.000)}
\label{fig:mnist-single-ranking-double-layer}
\end{figure}

@@

\subsubsection{iterative re-ranking Algorithm}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.49\linewidth]{mnist-deep-iterative-rerank-method.pdf}
\includegraphics[width=0.49\linewidth]{mnist-deep-iterative-rerank-accuracy.pdf}
\caption{Degradation in squared error (left) and classification accuracy (right) after pruning a 2-layer network using the iterative re-ranking algorithm; (\textbf{Network:} 2 layers, 50 neurons/layer, 10 outputs, logistic sigmoid activation, starting test accuracy: 1.000)}
\label{fig:mnist-re-ranking-double-layer}
\end{figure}

@@

\subsubsection{Visualization of brute force Pruning Decisions}
\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{mnist-deep-gt-gain.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the brute force criterion; (\textbf{Network:} 2 layers, 50 neurons/layer, 10 outputs, logistic sigmoid activation, starting test accuracy: 1.000)}
\label{fig:mnist-gt-double-layer}
\end{figure}

@@

\subsubsection{Visualization of 1st Order Approximation Pruning Decisions}
\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{mnist-deep-g1-gain.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the 1st order Taylor Series error approximation criterion; (\textbf{Network:} 2 layers, 50 neurons/layer, 10 outputs, logistic sigmoid activation, starting test accuracy: 1.000)}
\label{fig:mnist-g1-double-layer}
\end{figure}

@@

\subsubsection{Visualization of 2nd Order Approximation Pruning Decisions}
\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{mnist-deep-g2-gain.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the 2nd order Taylor Series error approximation criterion; (\textbf{Network:} 2 layers, 50 neurons/layer, 10 outputs, logistic sigmoid activation, starting test accuracy: 1.000)}
\label{fig:mnist-g2-double-layer}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\linewidth]{mnist-test-single-digit-0.pdf}
\caption{Degradation in squared error after pruning a single-layer network trained to do a one-versus-all classification of the digit 0 using the iterative re-ranking algorithm}
\label{fig:mnist-test-single-digit-0}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{mnist-test-single-digit-0-gt.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the brute force iterative re-ranking removal criterion}
\label{fig:mnist-test-single-digit-0-gt}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{mnist-test-single-digit-0-g1.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the first-order iterative re-ranking removal criterion}
\label{fig:mnist-test-single-digit-0-g1}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{mnist-test-single-digit-0-g2.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the second-order iterative re-ranking removal criterion}
\label{fig:mnist-test-single-digit-0-g2}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\linewidth]{mnist-test-single-digit-1.pdf}
\caption{Degradation in squared error after pruning a single-layer network trained to do a one-versus-all classification of the digit 1 using the iterative re-ranking algorithm}
\label{fig:mnist-test-single-digit-1}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{mnist-test-single-digit-1-gt.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the brute force iterative re-ranking removal criterion}
\label{fig:mnist-test-single-digit-1-gt}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{mnist-test-single-digit-1-g1.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the first-order iterative re-ranking removal criterion}
\label{fig:mnist-test-single-digit-1-g1}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{mnist-test-single-digit-1-g2.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the second-order iterative re-ranking removal criterion}
\label{fig:mnist-test-single-digit-1-g2}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\linewidth]{mnist-test-single-digit-2.pdf}
\caption{Degradation in squared error after pruning a single-layer network trained to do a one-versus-all classification of the digit 2 using the iterative re-ranking algorithm}
\label{fig:mnist-test-single-digit-2}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{mnist-test-single-digit-2-gt.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the brute force iterative re-ranking removal criterion}
\label{fig:mnist-test-single-digit-2-gt}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{mnist-test-single-digit-2-g1.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the first-order iterative re-ranking removal criterion}
\label{fig:mnist-test-single-digit-2-g1}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{mnist-test-single-digit-2-g2.pdf}
\caption{Error surface of the network output in log space (left) and real space (right) with respect to each candidate neuron chosen for removal using the second-order iterative re-ranking removal criterion}
\label{fig:mnist-test-single-digit-2-g2}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.49\linewidth]{diamond-iterative-rerank-method.pdf}
\includegraphics[width=0.49\linewidth]{diamond-iterative-rerank-accuracy.pdf}
\includegraphics[width=0.49\linewidth]{rshape-iterative-rerank-method.pdf}
\includegraphics[width=0.49\linewidth]{rshape-iterative-rerank-accuracy.pdf}
\caption{Degradation in squared error (left) and classification accuracy (right) after pruning a 2-layer network using the iterative re-ranking algorithm on a toy ``diamond'' shape dataset (top) and a toy ``random shape'' dataset (below); (\textbf{Network:} 2 layers, 50 neurons/layer, 10 outputs, logistic sigmoid activation, starting test accuracy: 0.992(diamond); 0.986(random shape)}
\label{fig:diamond}
\end{figure}
